### 2014-09-06 abstract.tex
good shape now

\begin{abstract}
Predictive analysis has recently emerged as a promising technique for 
sound detection of multithreading bugs (i.e., without false alarms). 
The idea is to start from an instrumented execution trace, and transform 
it based on the concrete information it provides, such as concrete values 
and memory accesses, to expose bugs, while preserving feasibility. For
example, it may reoder trace events to simulate different thread schedules, 
as long as flow dependencies are preserved.
Predictive analysis has been successfully applied to data-race detection, 
although the state-of-the-art techniques are overly restrictive in the 
transformations they allow such that their analysis coverage is 
unnecessarily limited. 
%so as to guarantee feasibility 
%and consequently also soundness. In particular, existing techniques (i) do not permit flow dependencies to be violated (except in very specific cases), and (ii) are unable to analyze execution paths beyond that of the input trace.
In this paper, we present \sysname, a predictive race detector that has two
important relaxations: value and path relaxations without affecting the
soundness guarantee. The former allows 
variables to have different values and the latter allows exploring 
unexecuted paths that are neighbors to the traced path.
% both of these restrictions while guaranteeing soundness, as we prove formally. Thanks to its ability to explore unexecuted branches as well as event orderings that violate flow dependencies, 
Our results show that \sysname\ is able to detect x$2.5$ more data races on a 
representative set of large-scale benchmarks compared to the state-of-the-art.
%in predictive race detection.
\end{abstract}

>>>>

\begin{abstract}
Predictive analysis has recently emerged as a promising technique for 
sound detection of multithreading bugs (i.e., without false alarms). 
The idea is to start from an instrumented execution trace, and transform 
it based on the concrete information it provides, such as concrete values 
and memory accesses, to expose bugs, while preserving feasibility. For
example, it may reoder trace events to simulate different thread schedules, 
as long as value flow dependencies are preserved.

Predictive analysis has been successfully applied to data-race detection, 
although the state-of-the-art techniques are overly restrictive in the 
transformations they allow such that their analysis coverage is 
unnecessarily limited.

In this paper, we present \sysname, a predictive race detector that has two
important relaxations: value and path relaxations without affecting the
soundness guarantee. The former allows 
variables to have different values and the latter allows exploring 
unexecuted paths that are neighbors to the traced path.
Our results show that \sysname\ is able to detect $2.5X$ as many data races on a 
representative set of large-scale benchmarks as compared to the state-of-the-art.
%in predictive race detection.
\end{abstract}

### 2014-09-06 eval.tex
good shape now

@@

{\bf Evaluation Method} We conducted our experiments on a set of 16 
applications, which were also used to evaluate {\sf RV}. Specifically, 
the set includes large applications such as {\sf Jigsaw}, 
{\sf Xalan} and {\sf Lusearch}. To handle large applications that make 
use of reflection, we applied the {\sf Tamiflex} tool~\cite{tamiflex}, which 
replaces reflective calls with the concrete method invocations recorded 
in the observed run.
% for the purpose of effective static analysis.  
We omit the benchmark {\sf eclipse} because the current version 
of {\sf Tamiflex}  leads to abnormal execution after the instrumentation, 
which throws an exception when the main service is started. 
By applying \tool\  to the abnormal execution, we identify only 3 races, 
similarly to the report of RV~\cite{pldi14}.
In addition, the {\sf montecarlo} benchmark requires an external input 
that we downloaded from the internet and simplified. For the large 
applications, we utilized the most lightweight available configuration.

@@

First of all, {\sf Recipe} finds $>$150 more races than {\sf RV}. There 
are several reasons for that: (1) {\sf Recipe} can reason about the 
accesses in the un-executed paths, while {\sf RV} and {\sf Recipe-s} can 
only reason about the accesses in the executed paths. (2) {\sf Recipe} 
or {\sf Recipe-s} relax the scheduling even if it 
%breaks the inter-thread read/write dependence structure 
changes variable values in the observed run. {\sf Recipe} allows the 
majority of the shared reads, i.e., the reads of primitive values, 
to freely read a different value from a different write 
as long as the value leads to the same branch decisions. {\sf RV}, however, 
requires them to read the same values as in the observed run. (3) An 
critical optimization proposed by {\sf RV} is to preserve dependences 
only for the reads before the preceding branches of the racy events, 
rather than all the reads. However, this optimization is underplayed 
by the fact that {\sf RV} introduces huge amount of artificial 
branches, i.e., one before each shared field access, which ensures 
the use of the same base objects.
We get rid of such artificial branches and instead, rely on the small 
amount of base read events to ensure the use of the same base 
objects (Section~\ref{sec:relax1} and Section~\ref{sec:relax2}). Our strategy reduces the number of branches 
greatly and amplifies the effectiveness of the optimization. We also 
carried out case studies (Section~\ref{sec:cases}) to better illustrate the scenarios.

Another interesting observation is that although {\sf Recipe} should 
produce all races found by {\sf RV} in theory, {\sf Recipe} may miss 
races found by {\sf RV} in practice (Column $Diff'$), i.e., {\sf Recipe} 
is not strictly more effective than {\sf RV} in practice. The reason  is 
the limitations of the underlying constraint solver: (1) the solver cannot 
compute constraints with very complex arithmatic operations, and (2) the 
solver does not support some program constants such as the scientific 
notation $3E-10$. In our empirical evaluation, we encounted only one 
benchmark, account, where these issues manifested.

@@

%TODO Reorder the columns: RV ReceipeS Recipe

\begin{table*}[htbp]
\caption{Relaxed Analysis}
\begin{flushleft}
\begin{tabular}{|l|r|r|r|r|l|r|r|r|r|r|r|r|r|r|}
\hline
 & \multicolumn{ 7}{c|}{Trace} & \multicolumn{ 3}{c|}{Races} & \multicolumn{ 2}{c|}{Difference} & \multicolumn{ 2}{c|}{Running time (sec)} \\ \hline
Benchmarks & \multicolumn{1}{l|}{Th} & \multicolumn{1}{l|}{Reads} & \multicolumn{1}{l|}{Writes} & \multicolumn{1}{l|}{Base} & Br & \multicolumn{1}{l|}{sync} & \multicolumn{1}{l|}{Total} & \multicolumn{1}{l|}{Recipe-s} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{RV} & \multicolumn{1}{l|}{Diff} & \multicolumn{1}{l|}{Diff'} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{RV} \\ \hline
critical & 3 & 13 & 7 & 5 & 2/13 & 6 & 78 & 8 & 8 & 8 & \multicolumn{1}{c|}{0} & 0 & 8 & \multicolumn{1}{c|}{2} \\ \hline
airline & 11 & 45 & 15 & 4 & 32/82 & 30 & 317 & 9 & 9 & 9 & 0 & 0 & 490 & 4 \\ \hline
account & 3 & 46 & 21 & 10 & 3/47 & 6 & 227 & 2 & 5 & 5 & 3 & 3 & 41 & 4 \\ \hline
pingpong & 4 & 7 & 7 & 3 & 0/15 & 6 & 111 & 1 & 1 & 1 & 0 & 0 & 19 & 1 \\ \hline
bbuffer & 4 & 640 & 118 & 10 & 634/1.1K & 217 & 3.3K & 13 & 25 & 9 & 21 & 5 & 62 & 5 \\ \hline
bubblesort & 26 & 1.3k & 966 & 121 & 155/2.8K & 322 & 8.4K & 7 & 7 & 7 & 0 & 0 & 3295 & 3 \\ \hline
bufwriter & 5 & 165 & 52 & 75 & 16/130 & 44 & 525 & 4 & 10 & 2 & 8 & 0 & 63 & 9 \\ \hline
mergesort & 5 & 38 & 33 & 5 & 15/472 & 28 & 1.7K & 3 & 10 & 3 & 10 & 0 & 37 & 5 \\ \hline
raytracer & 2 & 31 & 5 & 12 & 314/8,2K & 676 & 94.5K & 4 & 6 & 4 & 2 & 0 & 47 & 2 \\ \hline
montecarlo & 2 & 5 & 86 & 2 & 1.9K/38.2K & 21.1K & 1.9M & 1 & 4 & 1 & 3 & 0 & 1 & 17 \\ \hline
moldyn & 2 & 605 & 61 & 104 & 19.6K/52.6K & 62 & 203.4K & 6 & 14 & 2 & 12 & 0 & 2842 & 1 \\ \hline
ftpserver & 28 & 684 & 299 & 71 & 4.4K/233.3K & 78.2K & 3.9M & 99 & 152 & 57 & 108 & 13 & 811 & 153 \\ \hline
jigsaw & 12 & 525 & 702 & 211 & 63.2K/467.9K & 86.7K & 5.5M & 17 & 23 & 8 & 15 & 0 & 33 & 7 \\ \hline
sunflow & 9 & \multicolumn{1}{l|}{2.1K} & \multicolumn{1}{l|}{1.3K} & 473 & 201.3K/827.0K & 50K & \multicolumn{1}{l|}{7.1M} & 38 & 78 & 20 & 69 & 11 & 4520 & 22 \\ \hline
xalan & 9 & \multicolumn{1}{l|}{1.4K} & \multicolumn{1}{l|}{0.9K} & 209 & 15.7K/103.2K & \multicolumn{1}{l|}{190.1K} & \multicolumn{1}{l|}{6.6M} & 2 & 6 & 2 & 4 & 0 & 5317 & 10 \\ \hline
lusearch & 10 & \multicolumn{1}{l|}{2.3K} & \multicolumn{1}{l|}{0.5K} & 715 & 22.2K/164K & \multicolumn{1}{l|}{93.2K} & \multicolumn{1}{l|}{9.1M} & 27 & 49 & 14 & 38 & 5 & 5430 & 8 \\ \hline
\end{tabular}
\end{flushleft}
\label{tab:main}
\end{table*}

@@

{\bf Relaxing the Paths\ } Figure~\ref{fig:relax2} demonstrates how our 
approach relaxes the scheduling to account for  unexecuted paths in 
{\tt mergesort}. 
All threads invoke the method {\sf Sorting}, which recursively starts 
two child threads if there are two more available entries in the 
thread pool (lines 8-11), or starts one child thread if there is only 
one available entry (lines 4-5).  The availability is computed through 
the static method {\sf available} with the constant {\tt total}, which is equal to 5. The shared variable {\tt alive} denotes the used entries.

@@

\section{Threats to Validity}
A Java method can consist of up to 65535 bytecode instructions. Therefore,
 we count the number of bytecode instructions inside each method. If the 
resulting number exceeds 65525, we avoid instrumenting the method. 
The consequence is that we will potentially miss races inside a method for 
which we skipped instrumentation. In this case, we specify the variables 
read from the method to be equal to their concrete values in the constraints. 
The constraint solver can proceed safely without being affected by 
such methods.

\tool lacks support for certain operators. In our current 
implementation, we do not support bit operations such as $\&$ and $<<$, which accounts for most of our misses.

>>>>

%Besides, we terminate the monitoring run with a shutdown hook if it is beyond 30 minutes.

@@

{\bf Evaluation Method} We conducted our experiments on a set of 16 
applications, which were also used to evaluate {\sf RV}. Specifically, 
the set includes large applications such as {\sf Jigsaw}, 
{\sf Xalan} and {\sf Lusearch}. To handle large applications that make 
use of reflection, we applied the {\sf Tamiflex} tool~\cite{tamiflex}, which 
replaces reflective calls with the concrete method invocations recorded 
in the observed run.
% for the purpose of effective static analysis.  
We omit the benchmark {\sf eclipse} because the current version 
of {\sf Tamiflex}  leads to abnormal execution after the instrumentation, 
which throws an exception when the main service is started. 
By applying \tool\  to the abnormal execution, we identify only 3 races, 
similarly to the report of RV~\cite{pldi14}.
In addition, the {\sf montecarlo} benchmark requires an external input 
that we downloaded from the internet and simplified. For the large 
applications, we utilized the most lightweight available configuration.
To further control the cost of our experiments, we monitored each execution for at most 10 minutes.

@@

First of all, {\sf Recipe} finds $>$250 more races than {\sf RV}. There 
are several reasons for that: (1) {\sf Recipe} can reason about the 
accesses in the un-executed paths, while {\sf RV} and {\sf Recipe-s} can 
only reason about the accesses in the executed paths. (2) {\sf Recipe} 
or {\sf Recipe-s} relax the scheduling even if it 
%breaks the inter-thread read/write dependence structure 
changes variable values in the observed run. {\sf Recipe} allows the 
majority of the shared reads, i.e., the reads of primitive values, 
to freely read a different value from a different write 
as long as the value leads to the same branch decisions. {\sf RV}, however, 
requires them to read the same values as in the observed run. (3) A
critical optimization proposed by {\sf RV} is to preserve dependences 
only for the reads before the preceding branches of the racy events, 
rather than all the reads. However, this optimization is underplayed 
by the fact that {\sf RV} introduces huge amount of artificial 
branches, i.e., one before each shared field access, which ensures 
the use of the same base objects.
We get rid of such artificial branches and instead, rely on the small 
amount of base read events to ensure the use of the same base 
objects (Section~\ref{sec:relax1} and Section~\ref{sec:relax2}). Our strategy reduces the number of branches 
greatly and amplifies the effectiveness of the optimization. We also 
carried out case studies (Section~\ref{sec:cases}) to better illustrate the scenarios.

Another interesting observation is that although {\sf Recipe} should 
produce all races found by {\sf RV} in theory, {\sf Recipe} may miss 
races found by {\sf RV} in practice (Column $Diff'$), i.e., {\sf Recipe} 
is not strictly more effective than {\sf RV} in practice. The reason  is 
the limitations of the underlying constraint solver: (1) the solver cannot 
compute constraints with very complex arithmetic operations, and (2) the 
solver does not support some program constants such as the scientific 
notation $3E-10$. In our empirical evaluation, we encountered only one 
benchmark, {\sf account}, where these issues affect our detection capability.

@@

\begin{table*}[htbp]
\caption{Relaxed Analysis}
\begin{tabular}{|l|r|r|r|r|l|r|r|r|r|r|r|r|r|r|}
\hline
 & \multicolumn{ 7}{c|}{Trace} & \multicolumn{ 3}{c|}{Races} & \multicolumn{ 2}{c|}{Difference} & \multicolumn{ 2}{c|}{Running time (sec)} \\ \hline
Benchmarks & \multicolumn{1}{l|}{Th} & \multicolumn{1}{l|}{Reads} & \multicolumn{1}{l|}{Writes} & \multicolumn{1}{l|}{Base} & Br & \multicolumn{1}{l|}{sync} & \multicolumn{1}{l|}{Total} & \multicolumn{1}{l|}{RV} & \multicolumn{1}{l|}{Recipe-s} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{Diff} & \multicolumn{1}{l|}{Diff'} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{RV} \\ \hline
critical & 3 & 13 & 7 & 5 & 2/13 & 6 & 78 & 8 & 8 & 8 & 0 & 0 & 8 & 2 \\ \hline
airline & 11 & 45 & 15 & 4 & 32/82 & 30 & 317 & 9 & 9 & 9 & 0 & 0 & 490 & 4 \\ \hline
account & 3 & 46 & 21 & 10 & 3/47 & 6 & 227 & 5 & 2 & 5 & 3 & 3 & 41 & 4 \\ \hline
pingpong & 4 & 7 & 7 & 3 & 0/15 & 6 & 111 & 1 & 1 & 1 & 0 & 0 & 19 & 1 \\ \hline
bbuffer & 4 & 640 & 118 & 10 & 634/1.1K & 217 & 3.3K & 9 & 13 & 25 & 21 & 5 & 62 & 5 \\ \hline
bubblesort & 26 & 1.3k & 966 & 121 & 155/2.8K & 322 & 8.4K & 7 & 7 & 7 & 0 & 0 & 3295 & 3 \\ \hline
bufwriter & 5 & 165 & 52 & 75 & 16/130 & 44 & 525 & 2 & 4 & 10 & 8 & 0 & 63 & 9 \\ \hline
mergesort & 5 & 38 & 33 & 5 & 15/472 & 28 & 1.7K & 3 & 3 & 10 & 7 & 0 & 37 & 5 \\ \hline
raytracer & 2 & 31 & 5 & 12 & 314/8,2K & 676 & 94.5K & 4 & 4 & 6 & 2 & 0 & 47 & 2 \\ \hline
montecarlo & 2 & 5 & 86 & 2 & 1.9K/38.2K & 21.1K & 1.9M & 1 & 1 & 4 & 3 & 0 & 1 & 17 \\ \hline
moldyn & 2 & 605 & 61 & 104 & 19.6K/52.6K & 62 & 203.4K & 2 & 6 & 14 & 12 & 0 & 2842 & 1 \\ \hline
ftpserver & 28 & 684 & 299 & 71 & 4.4K/233.3K & 78.2K & 3.9M & 57 & 99 & 152 & 108 & 13 & 811 & 153 \\ \hline
jigsaw & 12 & 525 & 702 & 211 & 63.2K/467.9K & 86.7K & 5.5M & 8 & 17 & 23 & 15 & 0 & 33 & 7 \\ \hline
sunflow & 9 & 2.1K & 1.3K & 473 & 201.3K/827.0K & 50K & 7.1M & 20 & 38 & 78 & 69 & 11 & 4520 & 22 \\ \hline
xalan & 9 & 1.4K & 0.9K & 209 & 15.7K/103.2K & 190.1K & 6.6M & 2 & 2 & 6 & 4 & 0 & 5317 & 10 \\ \hline
lusearch & 10 & 2.3K & 0.5K & 715 & 22.2K/164K & 93.2K & 9.1M & 14 & 27 & 49 & 38 & 3 & 5430 & 8 \\ \hline
\end{tabular}
\label{tab:main}
\end{table*}

%\begin{table*}[htbp]
%\caption{Relaxed Analysis}
%\begin{flushleft}
%\begin{tabular}{|l|r|r|r|r|l|r|r|r|r|r|r|r|r|r|}
%\hline
% & \multicolumn{ 7}{c|}{Trace} & \multicolumn{ 3}{c|}{Races} & \multicolumn{ 2}{c|}{Difference} & \multicolumn{ 2}{c|}{Running time (sec)} \\ \hline
%Benchmarks & \multicolumn{1}{l|}{Th} & \multicolumn{1}{l|}{Reads} & \multicolumn{1}{l|}{Writes} & \multicolumn{1}{l|}{Base} & Br & \multicolumn{1}{l|}{sync} & \multicolumn{1}{l|}{Total} & \multicolumn{1}{l|}{Recipe-s} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{RV} & \multicolumn{1}{l|}{Diff} & \multicolumn{1}{l|}{Diff'} & \multicolumn{1}{l|}{Recipe} & \multicolumn{1}{l|}{RV} \\ \hline
%critical & 3 & 13 & 7 & 5 & 2/13 & 6 & 78 & 8 & 8 & 8 & \multicolumn{1}{c|}{0} & 0 & 8 & \multicolumn{1}{c|}{2} \\ \hline
%airline & 11 & 45 & 15 & 4 & 32/82 & 30 & 317 & 9 & 9 & 9 & 0 & 0 & 490 & 4 \\ \hline
%account & 3 & 46 & 21 & 10 & 3/47 & 6 & 227 & 2 & 5 & 5 & 3 & 3 & 41 & 4 \\ \hline
%pingpong & 4 & 7 & 7 & 3 & 0/15 & 6 & 111 & 1 & 1 & 1 & 0 & 0 & 19 & 1 \\ \hline
%bbuffer & 4 & 640 & 118 & 10 & 634/1.1K & 217 & 3.3K & 13 & 25 & 9 & 21 & 5 & 62 & 5 \\ \hline
%bubblesort & 26 & 1.3K & 966 & 121 & 155/2.8K & 322 & 8.4K & 7 & 7 & 7 & 0 & 0 & 3295 & 3 \\ \hline
%bufwriter & 5 & 165 & 52 & 75 & 16/130 & 44 & 525 & 4 & 10 & 2 & 8 & 0 & 63 & 9 \\ \hline
%mergesort & 5 & 38 & 33 & 5 & 15/472 & 28 & 1.7K & 3 & 10 & 3 & 10 & 0 & 37 & 5 \\ \hline
%raytracer & 2 & 31 & 5 & 12 & 314/8,2K & 676 & 94.5K & 4 & 6 & 4 & 2 & 0 & 47 & 2 \\ \hline
%montecarlo & 2 & 5 & 86 & 2 & 1.9K/38.2K & 21.1K & 1.9M & 1 & 4 & 1 & 3 & 0 & 1 & 17 \\ \hline
%moldyn & 2 & 605 & 61 & 104 & 19.6K/52.6K & 62 & 203.4K & 6 & 14 & 2 & 12 & 0 & 2842 & 1 \\ \hline
%ftpserver & 28 & 684 & 299 & 71 & 4.4K/233.3K & 78.2K & 3.9M & 99 & 152 & 57 & 108 & 13 & 811 & 153 \\ \hline
%jigsaw & 12 & 525 & 702 & 211 & 63.2K/467.9K & 86.7K & 5.5M & 17 & 23 & 8 & 15 & 0 & 33 & 7 \\ \hline
%sunflow & 9 & \multicolumn{1}{l|}{2.1K} & \multicolumn{1}{l|}{1.3K} & 473 & 201.3K/827.0K & 50K & \multicolumn{1}{l|}{7.1M} & 38 & 78 & 20 & 69 & 11 & 4520 & 22 \\ \hline
%xalan & 9 & \multicolumn{1}{l|}{1.4K} & \multicolumn{1}{l|}{0.9K} & 209 & 15.7K/103.2K & \multicolumn{1}{l|}{190.1K} & \multicolumn{1}{l|}{6.6M} & 2 & 6 & 2 & 4 & 0 & 5317 & 10 \\ \hline
%lusearch & 10 & \multicolumn{1}{l|}{2.3K} & \multicolumn{1}{l|}{0.5K} & 715 & 22.2K/164K & \multicolumn{1}{l|}{93.2K} & \multicolumn{1}{l|}{9.1M} & 27 & 49 & 14 & 38 & 5 & 5430 & 8 \\ \hline
%\end{tabular}
%\end{flushleft}
%\label{tab:main}
%\end{table*}

@@

{\bf Relaxing the Paths\ } Figure~\ref{fig:relax2} demonstrates how our 
approach relaxes the scheduling to account for  unexecuted paths in 
{\tt mergesort}. 
All threads invoke the method {\sf Sorting}, which recursively starts 
two children threads if there are two more available entries in the 
thread pool (lines 8-11), or starts one child thread if there is only 
one available entry (lines 4-5).  The availability is computed through 
the static method {\sf available} with the constant {\tt total}, which is equal to 5. The shared variable {\tt alive} denotes the used entries.

@@

\section{Threats to Validity}
A Java method can consist of up to 65535 bytecode instructions. Therefore,
 we count the number of bytecode instructions inside each method. If the 
resulting number exceeds 65535, we avoid instrumenting the method. 
The consequence is that we will potentially miss races inside a method for 
which we skipped instrumentation. In this case, we specify the variables 
read from the method to be equal to their concrete values in the constraints. 
The constraint solver can proceed safely without being affected by 
such methods.

\tool\  lacks support for certain operators. In our current 
implementation, we do not support bit operations such as $\&$ and $<<$, which accounts for most of our misses.

### 2014-09-06 guarantee.tex
good shape now

First, to the best of our knowledge, none of the existing techniques 
automatically explore the un-executed branches by relaxing the schedules, whereas \tool enables this.
Second, assume we disable the exploration of un-executed branches and all 
techniques start with the same trace. Our technique still explores more 
traces. Figure~\ref{fig:discuss} illustrates the difference, where two 
vertical lines represent the progress of two threads and the circles 
with numbers denote events with ids. 
Existing techniques require the reads to read the same values, and hence
enforce the schedule order $e_5 \rightarrow e_6$ and $e_2\rightarrow e_3$. 
We allow the reads to read different values from different writes as long as 
the feasibility is preserved. Comparatively, we enforce a weaker 
schedule order  $e_4 \rightarrow e_6$ and $e_2\rightarrow e_3$, which 
allows more scheduling, e.g., the concurrent execution of $e_7$ (or 
some event after $e_7$) and $e_5$.

However, \tool has not reached the maximum bound of sound exploration.
% does not identify the maximal set of traces 
%from a single trace. 
The underlying reason is that, we still enforce the schedule for 
preserving the base object, e.g., $e_2\rightarrow e_3$. It is possible 
to further relax the schedule so that $e_3$ reads from $e_1$, but 
this requires challenging reasoning of the field accesses as their base 
objects become uncertain. We plan to explore this idea in future work.

>>>>

First, to the best of our knowledge, none of the existing techniques 
automatically explore the un-executed branches by relaxing the schedules, whereas \tool\  enables this.
Second, assume we disable the exploration of un-executed branches and all 
techniques start with the same trace. Our technique still explores more 
traces. Figure~\ref{fig:discuss} illustrates the difference, where two 
vertical lines represent the progress of two threads and the circles 
with numbers denote events with ids. 
Existing techniques require the reads to read the same values, and hence
enforce the schedule order $e_5 \rightarrow e_6$ and $e_2\rightarrow e_3$. 
We allow the reads to read different values from different writes as long as 
the feasibility is preserved. Comparatively, we enforce a weaker 
schedule order  $e_4 \rightarrow e_6$ and $e_2\rightarrow e_3$, which 
allows more scheduling, e.g., the concurrent execution of $e_7$ (or 
some event after $e_7$) and $e_5$.

However, \tool\  has not reached the maximum bound of sound exploration.
% does not identify the maximal set of traces 
%from a single trace. 
The underlying reason is that, we still enforce the schedule for 
preserving the base object, e.g., $e_2\rightarrow e_3$. It is possible 
to further relax the schedule so that $e_3$ reads from $e_1$, but 
this requires challenging reasoning of the field accesses as their base 
objects become uncertain. We plan to explore this idea in future work.

### 2014-09-06 introduction.tex
good shape now

%that is missed, as it involves the statements in red, is between lines {\tt 2} and {\tt 7}.
Therefore in this paper, we propose \sysname, a relaxed predictive analysis. We identify the critical runtime
informantion that needs to be preserved during trace perturbation and relax the remaining information. 
In particular, we preserve all the addresses de-referenced (e.g. heap and array accesses) in the original execution,
and some of the branch outcomes such that part of the thread local paths stay intact. The criterion is that
we forbid \sysname\ to explore an unexecuted branch if the effect of the branch cannot be precisely modeled
(e.g. an array element is read while it was not defined in the original trace). The essence of our technique 
is to {\em explore the neighborhood of the original execution as much as possible}. Due to the substantially
enlarged search space, our results show that a race detector based on our relaxed predictive analysis 
can detect XXX times more races than existing predictive analysis, while guaranteeing soundness.

Our contributions are summarized as follows.
\begin{itemize}
\item We propose to relax existing predictive analysis and identify a bound of relaxation (i.e. what can
be relaxed).
\item We develop a constraint encoding scheme that encodes the necessary information (i.e. the
part that must be preserved) and the relaxed information (i.e., the part that may be mutated) uniformly as part of a single logical representation.
\item We develop a propotype \sysname. Our results show XXX.
\end{itemize}

>>>>

%that is missed, as it involves the statements in red, is between lines {\tt 2} and {\tt 7}.
Therefore in this paper, we propose \sysname, a relaxed predictive analysis. We identify the critical runtime
informantion that needs to be preserved during trace perturbation and relax the remaining information. 
In particular, we preserve all the addresses de-referenced (e.g. heap and array accesses) in the original execution,
and some of the branch outcomes such that part of the thread local paths stay intact. The criterion is that
we forbid \sysname\ to explore an unexecuted branch if the effect of the branch cannot be precisely modeled
(e.g. an array element is read while it was not defined in the original trace). The essence of our technique 
is to {\em explore the neighborhood of the original execution as much as possible}. Due to the substantially
enlarged search space, our results show that a race detector based on our relaxed predictive analysis 
can detect $2.5X$ as many races as the existing predictive analysis, while guaranteeing soundness.

Our contributions are summarized as follows.
\begin{itemize}
\item We propose to relax existing predictive analysis and identify a bound of relaxation (i.e. what can
be relaxed).
\item We develop a constraint encoding scheme that encodes the necessary information (i.e. the
part that must be preserved) and the relaxed information (i.e., the part that may be mutated) uniformly as part of a single logical representation.
\item We develop a propotype \sysname. Our results on 16 benchmarks show \sysname is significantly more effective than existing predictive analyses. We also conducted case studies to confirm the effectiveness.
\end{itemize}
